### 2025-07-23 machine-learning.qmd
20250722 - tweaks

We use the optimal parameters identified during tuning.
We use a low learning rate (0.1) to avoid overfitting.
We set some light regularization (`lambda_l2`) for better generalization.
We also set the maximum tree depth (`max_depth`) at 5 to capture complex (up to 5-way) interactions, and set the maximum number of terminal nodes (`num_leaves`) per tree at 2^6 (64)—though the number will not reach greater than $2^\text{max_depth} = 2^5 = 32$.
We set the minimum number of samples in any leaf (`min_data_in_leaf`) to be 100.

@@

>>>>

We use the optimal parameters identified during tuning.
We use a low learning rate (0.1) to avoid overfitting.
We set some light regularization (`lambda_l2`) for better generalization.
We also set the maximum tree depth (`max_depth`) at 5 to capture complex (up to 5-way) interactions, and set the maximum number of terminal nodes (`num_leaves`) per tree at $2^6$ (64)—though the number will not reach greater than $2^{\text{max_depth}} = 2^5 = 32$.
We set the minimum number of samples in any leaf (`min_data_in_leaf`) to be 100.

@@

@fig-treeBoostingModel depicts the predicted versus actual fantasy points for the model on the test data.

```{r}
#| label: fig-treeBoostingModel
#| fig-cap: "Predicted Versus Actual Fantasy Points for Tree-Boosting Model."
#| fig-alt: "Predicted Versus Actual Fantasy Points for Tree-Boosting Model."

# Calculate combined range for axes
axis_limits <- range(c(predictedVsActual$predictedPoints, predictedVsActual$actualPoints), na.rm = TRUE)

ggplot(
  predictedVsActual,
  aes(
    x = predictedPoints,
    y = actualPoints)) +
  geom_point(
    size = 2,
    alpha = 0.6) +
  geom_abline(
    slope = 1,
    intercept = 0,
    color = "blue",
    linetype = "dashed") +
  coord_equal(
    xlim = axis_limits,
    ylim = axis_limits) +
  labs(
    title = "Predicted vs Actual Fantasy Points (Test Data)",
    x = "Predicted Fantasy Points",
    y = "Actual Fantasy Points"
  ) +
  theme_classic() +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```
